% created on 09-04-2020
% @author : ebazan
\titlespacing*{name=\chapter,numberless}{0pt}{0pt}{40pt}
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgments}

These almost four years of thesis work have been a great experience both professionally and personally in my life. Along the way, I have met very valuable people whom I would like to thank because the Ph.D. would not have been what it has become without them.

 First of all, I thank my thesis directors for accepting the challenge of guiding and introducing someone from the robotics area to the world of mathematical morphology. Thank you for trusting me and for the excellent guidance during this thesis and throughout the writing of this manuscript. I also thank M. Thierry Géraud and M. Petr Matula for agreeing to review my manuscript and be part of my jury; and Mme. Valery Naranjo, M. Gerardo Flores, and M. Nicolas Passat for agreeing to be part of my jury. 

 I also thank Anne-Marie and the great family of the CMM: Béa, Michel, Etienne, Samy, Bruno, Santi, Jesus, Jose-Marcio and François W. Thank you for the conversations about everything and nothing during coffee breaks and extracurricular activities, all that made me feel less far from home.

 Without a doubt, I cannot but thank the group of Ph.D. students from DOPAMINES and CMM who introduced me (and continue to introduce me) to French culture: Laure, Jean, Marine, Aurelien, Pierre S., Albane, Kaïwen, Seb, Théo, Leo, David, Élodie, Francois, Nico, Robin, Bob Julien, Valentin, Mike, Ricardo, Alan, Bibiche, Tarek, Mateus, Angelique, etc. I really appreciated those beer times at the Glasgow, the tarot games, and the random and weird conversations that I occasionally did not understand.

 To the people of the group of Hippies and Put1 Vegans (formerly Malakas) and other people I met during this time: Anais, Andrés, Fanny, Théo, Lydia, Benj, Élise, Mauro, Carol, Vincent, Cyril, Élsa, Sophie, Bassam, Pao, David, Laura. Thank you for becoming my new family and for your support during the bad times, but above all for the joys and all the good times we had.

 Thanks to Chimpo for all her love and support throughout this thesis and to my family in Mexico, especially my parents Leonardo and Bertha and my sister Jocelyn for being so strong and supportive of my decision to do my Ph.D. abroad.

 Finally, I thank CONACyT, the Center for Mathematical Morphology, and the ESSIE Paris for the financial support during the thesis work.