% created on 19/02/2021
% @author : ebazan

\chapter*{Scientific contributions and personal publications}\label{ch:publications}

\begin{itemize}
    \item [\textbf{W4}] Bazán E., Dokládal P., Dokládalová E. \textit{Learning Perceptual Importance of Color and Texture for Unsupervised Segmentation}. Oral communication presented at the French-German Doctoral Workshop, Kaiserslautern, Germany, Oct. 2019.
    \item [\textbf{C2}] Bazán E., Dokládal P., Dokládalová E. \textit{Quantitative Analysis of Similarity Measures of Distributions}. The British Machine Vision Conference (BMVC), Cardiff, U.K., Sep. 2019.
    \item [\textbf{W3}] Bazán E., Dokládal P., Dokládalová E. \textit{Vision Methods for Aerial Vehicles’ Autonomous Navigation}. Oral communication presented at the Optics Research Center, León, Guanajuato, México, Feb. 2019.
    \item [\textbf{W2}] Bazán E., Dokládal P., Dokládalová E. \textit{The Optimal Transport for Image Segmentation}. Oral communication presented at the French-German Doctoral Workshop, Fontainebleau, France, Nov. 2018.
    \item [\textbf{C1}] Bazán E., Dokládal P., Dokládalová E. U\textit{nsupervised Perception Model for UAVs Landing Target Detection and Recognition}. Advanced Concepts for Intelligent Vision Systems. ACIVS,  Sep. 2018.
    \item [\textbf{W1}] Bazán E., Dokládal P., Dokládalová E. \textit{Non supervised perceptual model for target recognition in UAVs}. Reconnaissance des Formes, Image, Apprentissage et Perception RFIAP, Jun. 2018.
\end{itemize}
